---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# BradleyTerry2

[![CRAN_Status_Badge](https://www.r-pkg.org/badges/version/BradleyTerry2)](https://cran.r-project.org/package=BradleyTerry2)

Specify and fit the Bradley-Terry model, including structured versions in which 
the parameters are related to explanatory variables through a linear predictor 
and versions with contest-specific effects, such as a home advantage.

## Installation

You can install **BradleyTerry2** from github with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("hturner/BradleyTerry2")
```

## Code of conduct

Please note that this project is released with a 
[Contributor Code of Conduct](https://github.com/hturner/BradleyTerry2/blob/master/CONDUCT.md). By participating in this project you 
agree to abide by its terms.